---
title: "Transforming Pea data into observed data for sims discovery science"
author: "R Zyskowski , Adrain Hunt"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: yes
  html_document: default
    
---

## Step one read data from Excel File

Key processes:

- Reads  *Technically correct* data into `data.frame`

- Combines the Lincoln & Hawkes bay data


#### Data management

```{r, results='hide', echo=FALSE, include=FALSE}

rm(list=setdiff(ls(), "source_rmd")) #remove all objects but "source_rmd" from the environment before assigning the new objects .. this is especially included to use this script as a child script in the MainScript.Rmd file 

#rm(list = ls(all = TRUE))

```

Load the required libraries.


```{r, warning=FALSE}
# load the required libraries
library(lubridate)
library(plyr);library(dplyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr) #required to use the pipe (%>%) operator
library(readxl)
library(tidyverse)

```


** Set the directories and Data File**
```{r}
url <- "https://iplant.plantandfood.co.nz/project/P442060-13/_layouts/15/WopiFrame.aspx?sourcedoc=/project/P442060-13/Research/18_19_SAE_pea_protein_managment.xlsx&action=default"

Source_HB = "RAW_HB"
Source_Linc = "RAW_Lincoln"

```


### Create the Raw Data files


```{r}
source(file = "../IplantScrape.r") #source scraper function 

df_RAW_Lincoln<- scrape_xl(url, sheet = Source_Linc, skip = 2)
df_RAW_HB<- scrape_xl(url, sheet =  Source_HB, skip = 2)


df_RAW_HB$Index  <- NULL
df_RAW_Lincoln$Index  <- NULL
#name contains &
names(df_RAW_Lincoln)[38] <- "FinalPodPeaFW"

```

#### Inspection of loaded data set

```{r}
#Retrieve the classes of all columns in a data.frame 
str(df_RAW_Lincoln)
```



```{r}
str(df_RAW_HB)
```



```{r}
summary(df_RAW_HB)
```





```{r}
head(df_RAW_HB)
```


### Removing rows with NAs (missing values) in `data.frame`

```{r}
# Remove rows with NAs in data.frame
#df_HBData <- df_RAW_HB[!complete.cases(df_RAW_HB), ]
df_HBData <- df_RAW_HB
na.omit(df_HBData)

df_LincolnData <- df_RAW_Lincoln
na.omit(df_LincolnData)

#head(df_HBData)

```

### Add column Represeint Site
```{r}
df_HBData$Site = "HawkesBay"
df_LincolnData$Site = "Lincoln"

```
```{r}
df_HBData$partFW <- as.numeric(as.character(df_HBData$partFW)) 
df_HBData$maturepodFW <- as.numeric(as.character(df_HBData$maturepodFW)) 
df_HBData$maturepodDW <- as.numeric(as.character(df_HBData$maturepodDW)) 
df_LincolnData$maturepodFW <- as.numeric(as.character(df_LincolnData$maturepodDW)) 


```

### Merge the Two Dataframes based on Common factors
```{r}
df_CombinedData  <- bind_rows(df_HBData,df_LincolnData)

head(df_CombinedData)

```
### Fix up Columns to match Both
```{r}
# Sample Fresh Weight
   # we need to know the Fesh weight of the sample for the measure area.
df_CombinedData$SampleFW = df_CombinedData$TFW

   # we need to know how much of the partition was used for subsample
df_CombinedData$PARTFW = df_CombinedData$partFW


for (k in 1:length(df_CombinedData$TFW) ) #any column will do for length
 {
  #Choose out of FW1 & 2 for HB
  if (is.na(df_CombinedData$TFW2[k]) == FALSE)
  {
    if (is.na(df_CombinedData$TFW[k]) == TRUE)
      {
       df_CombinedData$SampleFW[k] = df_CombinedData$TFW2[k] 
      }
  }
  
  #if final harvest
  #HB
  if (isTRUE( df_CombinedData$Final_residueFW[k] > 0) )       
   {
   
    df_CombinedData$PARTFW[k] = ((df_CombinedData$Final_residueFW[k] + df_CombinedData$Final_podFW[k] +df_CombinedData$Final_grainFW[k]))# + df_CombinedData$Final_grainSprouted[k]))
   }
  #lincoln
  if (isTRUE( df_CombinedData$Final_ResidueSubFW[k] > 0) )       
   {
   
    df_CombinedData$PARTFW[k] = ((df_CombinedData$Final_ResidueSubFW[k] + df_CombinedData$FinalPodPeaFW[k]))#+ df_CombinedData$Final_grainSprouted[k]))
   }
 
}



#SampleDW

# leaf & stem
df_CombinedData$SampleLeafDW <- df_CombinedData$greenleafDW
df_CombinedData$SampleStemDW <- df_CombinedData$greenstemDW

# Dead leaf and Stem
df_CombinedData$SampleDeadDW <- df_CombinedData$deadFW

for (k in 1:length(df_CombinedData$SampleDeadDW) ) #any column will do for length
 {
   if (is.na(df_CombinedData$SampleDeadDW[k]) == TRUE)
      {
       df_CombinedData$SampleDeadDW[k] = df_CombinedData$deadstemDW[k] + df_CombinedData$deadleafDW[k]
      }
    if (is.na(df_CombinedData$SampleDeadDW[k]) == TRUE)
      {
       df_CombinedData$SampleDeadDW[k] = 0
      }
   

 }
```



