---
title: "Transforming Pea data into observed data for sims discovery science"
author: "R Zyskowski , Adrain Hunt"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: yes
  html_document: default
    
---

## Step one read data from Excel File

Key processes:

- Reads  *Technically correct* data into `data.frame`

- Combines the Lincoln & Hawkes bay data


#### Data management

```{r, results='hide', echo=FALSE, include=FALSE}

rm(list=setdiff(ls(), "source_rmd")) #remove all objects but "source_rmd" from the environment before assigning the new objects .. this is especially included to use this script as a child script in the MainScript.Rmd file 

#rm(list = ls(all = TRUE))

```

Load the required libraries.


```{r, warning=FALSE}
# load the required libraries
library(lubridate)
library(plyr);library(dplyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr) #required to use the pipe (%>%) operator
library(readxl)
library(tidyverse)

```


** Set the directories and Data File**
```{r}
url <- "https://iplant.plantandfood.co.nz/project/P442060-13/_layouts/15/WopiFrame.aspx?sourcedoc=/project/P442060-13/Research/18_19_SAE_pea_protein_managment.xlsx&action=default"

Source_HB = "RAW_HB"
Source_Linc = "RAW_Lincoln"

```


### Create the Raw Data files


```{r}
source(file = "../IplantScrape.r") #source scraper function 

df_RAW_Lincoln<- scrape_xl(url, sheet = Source_Linc, skip = 2)
df_RAW_HB<- scrape_xl(url, sheet =  Source_HB, skip = 2)


df_RAW_HB$Index  <- NULL
df_RAW_Lincoln$Index  <- NULL
#name contains &
names(df_RAW_Lincoln)[38] <- "FinalPodPeaFW"
#set column as numeric
df_RAW_HB$partFW <- as.numeric(as.character(df_RAW_HB$partFW)) 


```

#### Inspection of loaded data set

```{r}
#Retrieve the classes of all columns in a data.frame 
str(df_RAW_Lincoln)
```



```{r}
str(df_RAW_HB)
```



```{r}
summary(df_RAW_HB)
```





```{r}
head(df_RAW_HB)
```


### Removing rows with NAs (missing values) in `data.frame`

```{r}
# Remove rows with NAs in data.frame
#df_HBData <- df_RAW_HB[!complete.cases(df_RAW_HB), ]
df_HBData <- df_RAW_HB
na.omit(df_HBData)

df_LincolnData <- df_RAW_Lincoln
na.omit(df_LincolnData)

#head(df_HBData)

```

### Add column Represeint Site
```{r}
df_HBData$Site = "HawkesBay"
df_LincolnData$Site = "Lincoln"

```
```{r}
df_HBData$partFW <- as.numeric(as.character(df_HBData$partFW)) 
df_HBData$maturepodFW <- as.numeric(as.character(df_HBData$maturepodFW)) 
df_HBData$maturepodDW <- as.numeric(as.character(df_HBData$maturepodDW)) 
df_LincolnData$maturepodFW <- as.numeric(as.character(df_LincolnData$maturepodDW)) 


```

### Merge the Two Dataframes based on Common factors
```{r}
df_CombinedData  <- bind_rows(df_HBData,df_LincolnData)

head(df_CombinedData)

```
### Fix up Columns to match Both
```{r}
# Sample Fresh Weight
   # we need to know the Fesh weight of the sample for the measure area.
df_CombinedData$SampleFW = df_CombinedData$TFW

   # we need to know how much of the partition was used for subsample
df_CombinedData$PARTFW = df_CombinedData$partFW


for (k in 1:length(df_CombinedData$TFW) ) #any column will do for length
 {
  #Choose out of FW1 & 2 for HB
  if (is.na(df_CombinedData$TFW2[k]) == FALSE)
  {
    if (is.na(df_CombinedData$TFW[k]) == TRUE)
      {
       df_CombinedData$SampleFW[k] = df_CombinedData$TFW2[k] 
      }
  }
  
  #if final harvest
  #HB
  if (isTRUE( df_CombinedData$Final_residueFW[k] > 0) )       
   {
   
    df_CombinedData$PARTFW[k] = ((df_CombinedData$Final_residueFW[k] + df_CombinedData$Final_podFW[k] +df_CombinedData$Final_grainFW[k]))# + df_CombinedData$Final_grainSprouted[k]))
   }
  #lincoln
  if (isTRUE( df_CombinedData$Final_ResidueSubFW[k] > 0) )       
   {
   
    df_CombinedData$PARTFW[k] = ((df_CombinedData$Final_ResidueSubFW[k] + df_CombinedData$FinalPodPeaFW[k]))#+ df_CombinedData$Final_grainSprouted[k]))
   }
 
}



#SampleDW

# leaf & stem
df_CombinedData$SampleLeafDW <- df_CombinedData$greenleafDW
df_CombinedData$SampleStemDW <- df_CombinedData$greenstemDW
df_CombinedData$SamplePodDW <- df_CombinedData$greenpodDW

# Dead leaf and Stem
df_CombinedData$SampleDeadDW <- df_CombinedData$deadFW

for (k in 1:length(df_CombinedData$SampleDeadDW) ) #any column will do for length
 {
   if (is.na(df_CombinedData$SampleDeadDW[k]) == TRUE)
      {
       df_CombinedData$SampleDeadDW[k] = df_CombinedData$deadstemDW[k] + df_CombinedData$deadleafDW[k]
      }
    if (is.na(df_CombinedData$SampleDeadDW[k]) == TRUE)
      {
       df_CombinedData$SampleDeadDW[k] = 0
      }
 

}

# Intermediate Grain 
df_CombinedData$SampleGWt = df_CombinedData$grainDW


for (k in 1:length(df_CombinedData$grainDW) ) #any column will do for length
 {
   if (is.na(df_CombinedData$grainDW[k]) ==TRUE)
   {
   
   if (is.na(df_CombinedData$greengrainDW[k]) == FALSE)
      {
       df_CombinedData$SampleGWt[k] =  df_CombinedData$greengrainDW[k]
      }

   #Add mature
      if (is.na(df_CombinedData$maturegrainDW[k]) == FALSE)
      {
       df_CombinedData$SampleGWt[k] = df_CombinedData$SampleGWt[k] + df_CombinedData$maturegrainDW[k]
      }
   }

}


#Total Pod/shell weight
 df_CombinedData$maturepodFW[is.na(df_CombinedData$maturepodFW)] <- 0
 df_CombinedData$maturepodDW[is.na(df_CombinedData$maturepodDW)] <- 0

 df_CombinedData <-  df_CombinedData %>%
   mutate(SampleShellWt = (greenpodDW+maturepodDW)) 


#Final grain Wt

 df_CombinedData$Final_grainSproutedDW[is.na(df_CombinedData$Final_grainSproutedDW)] <- 0 
 df_CombinedData$Final_grainFW[is.na(df_CombinedData$Final_grainFW)] <- 0
 df_CombinedData$grainDW[is.na(df_CombinedData$grainDW)] <- 0


# df_CombinedData$SampleGrainSprouted <- 0
# for (k in 1:length(df_CombinedData$Final_grainSproutedFW) ) #any column will do for length
#  {
#   if (is.na(df_CombinedData$Final_grainSproutedFW[k]) == FALSE)
#       {
#        df_CombinedData$SampleGrainSprouted[k] = df_CombinedData$Final_grainSproutedDW[k] * df_CombinedData$Final_grainFW[k]/df_CombinedData$Final_grainSproutedFW[k]
#       }
# 
#   }
# df_CombinedData <- df_CombinedData %>%
#   mutate(SampleFGW = ((Final_100grainDW*Final_grainFW/Final_100grainFW)))#+SampleGrainSprouted)) 
# 
# df_CombinedData$SampleFGW[is.nan(df_CombinedData$SampleFGW)] <- NA 
# df_CombinedData$SampleFGW[is.na(df_CombinedData$SampleFGW)] <- 0 
# 
# df_CombinedData$SampleGWt[is.nan(df_CombinedData$SampleGWt)] <- NA 
# df_CombinedData$SampleGWt[is.na(df_CombinedData$SampleGWt)] <- 0 

#Total grain wt
 
# let try it the % way
 
#% of grain that is spouted
df_CombinedData <-  df_CombinedData %>%
   mutate(SpoutedPC = (Final_grainSprouted/Final_GrainCount)) 
 
 df_CombinedData$SpoutedPC[is.na(df_CombinedData$SpoutedPC)] <- 0 
 
 df_CombinedData <- df_CombinedData %>%
   mutate(SampleAveWt = ((Final_100grainDW)/100))  # What is the non sprouted average weight
 
 
df_CombinedData <- df_CombinedData %>%
   mutate(SampleFGW = SampleAveWt * Final_GrainCount)  # What is sample total
 
 
 
 df_CombinedData$SampleGWt[is.nan(df_CombinedData$SampleGWt)] <- NA 
 df_CombinedData$SampleGWt[is.na(df_CombinedData$SampleGWt)] <- 0

df_CombinedData$SampleFGW[is.nan(df_CombinedData$SampleFGW)] <- NA 
 df_CombinedData$SampleFGW[is.na(df_CombinedData$SampleFGW)] <- 0

df_CombinedData <- df_CombinedData %>%  mutate(SampleGrainWT = (SampleFGW+ SampleGWt))

```

# have sample values - need plot values g/m2
```{r}
# Biomass
df_CombinedData <-  df_CombinedData %>%
   mutate(PC = (SampleFW/PARTFW)) %>%
   mutate(perM = (PC/HA)) %>%
   mutate(partDW = (SampleLeafDW + SampleStemDW + SampleDeadDW  + SamplePodDW + maturepodDW + SampleGrainWT)) %>%
   mutate(AboveGroundWt = (perM*partDW) )%>%
  mutate(leafLiveWt = perM*(SampleLeafDW)) %>%
   mutate(StemLiveWt = perM*(SampleStemDW)) %>%
  mutate(DeadWt = perM*(SampleDeadDW)) %>%
   mutate(PodLiveWt = perM*(SamplePodDW)) %>%
   mutate(ShellWt = perM*(SampleShellWt)) %>%
   mutate(GrainWt = (SampleGrainWT)/HA) %>%  #already done the PARTFW in above
   mutate(GrainLiveWt = perM*(SampleGWt)) 
   

# Green area

 df_CombinedData$SampleFGW[is.na(df_CombinedData$Leaf_area)] <- 0
 df_CombinedData$SampleFGW[is.na(df_CombinedData$Stem_area)] <- 0
 df_CombinedData$SampleFGW[is.na(df_CombinedData$Pod_area)] <- 0

 df_CombinedData <-  df_CombinedData %>%
   mutate(LeafArea = perM*(Leaf_area)) %>%  #cm2
   mutate(leafLAI = (LeafArea/10000)) %>% #m
   mutate(StemArea = perM*(Stem_area)) %>%  #cm2
   mutate(stemGAI = (StemArea/10000)) %>% #m
   mutate(PodArea = perM*(Pod_area)) %>%  #cm2
   mutate(podGAI = (PodArea/10000)) %>% #m
   mutate(GAI = (leafLAI + stemGAI+podGAI)) #m/m


```
### we have biomass so cancaluclate N levels

```{r}
#N content  
  
df_CombinedData$N_Content_Green_Leaf[df_CombinedData$N_Content_Green_Leaf == "-"] <- NA 

df_CombinedData$N_Content_Green_Leaf <- as.numeric(as.character(df_CombinedData$N_Content_Green_Leaf)) 

df_CombinedData$N_Content_Green_Stem[df_CombinedData$N_Content_Green_Stem == "-"] <- NA 

df_CombinedData$N_Content_Green_Stem <- as.numeric(as.character(df_CombinedData$N_Content_Green_Stem)) 

df_CombinedData$N_Content_Green_Grain[df_CombinedData$N_Content_Green_Grain == "-"] <- NA 
df_CombinedData$N_Content_Green_Grain <- as.numeric(as.character(df_CombinedData$N_Content_Green_Grain)) 
df_CombinedData$N_Content_Mat_Grain[df_CombinedData$N_Content_Mat_Grain == "-"] <- NA 
df_CombinedData$N_Content_Mat_Grain <- as.numeric(as.character(df_CombinedData$N_Content_Mat_Grain)) 

df_CombinedData$N_Content_Mat_Pod[df_CombinedData$N_Content_Mat_Grain == "-"] <- NA 
df_CombinedData$N_Content_Mat_Pod <- as.numeric(as.character(df_CombinedData$N_Content_Mat_Pod)) 

df_CombinedData$N_Content_Green_Pod[df_CombinedData$N_Content_Mat_Grain == "-"] <- NA 
df_CombinedData$N_Content_Green_Pod <- as.numeric(as.character(df_CombinedData$N_Content_Green_Pod)) 

 df_CombinedData <-  df_CombinedData %>%
    mutate(LeafNConc = N_Content_Green_Leaf/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(leafN = LeafNConc * leafLiveWt )
   
 df_CombinedData <-  df_CombinedData %>%
    mutate(StemNConc = N_Content_Green_Stem/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(StemN = StemNConc *StemLiveWt )

 df_CombinedData <-  df_CombinedData %>%
    mutate(GrainNConc = N_Content_Green_Grain/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(GrainLiveN = GrainNConc*GrainLiveWt )

  df_CombinedData <-  df_CombinedData %>%
    mutate(GrainMatureNConc = N_Content_Mat_Grain/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(GrainMatureN = GrainMatureNConc * GrainWt )
 
 df_CombinedData <-  df_CombinedData %>%
    mutate(PodNConc = N_Content_Green_Pod/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(PodLiveN = PodNConc*PodLiveWt )

  df_CombinedData <-  df_CombinedData %>%
    mutate(PodMatureNConc = N_Content_Mat_Pod/100.0)
 df_CombinedData <-  df_CombinedData %>%
    mutate(PodMatureN = PodMatureNConc * ShellWt )

 
```
# For testing purposes lets group the midnatch days at HB
```{r}
for (k in 1:length(df_CombinedData$Date) ) 
 {
   tmp <- df_CombinedData$Date[k] 
  if (isTRUE( tmp == as.Date("2019-01-25") ))       
#   if (tmp = "2019-01-25")  
   {
    df_CombinedData$Date[k] <- as.Date("2019-01-23")
   }

}


```

#Summary mean and se grouped by site, treatment and clock as function
```{r, sum_elemant function}

sum_it<- function(frame=df_CombinedData,var1 ){
  sum_mean<- df_CombinedData%>% 
  group_by(Date,Trt_name, Site) %>% 
  summarise_at(.vars = var1,funs(mean,se=sd(.)/sqrt(n())))
  
#print(sum_mean)
}


```

#sunction to draw line graphs with error bars
```{r, graphing function}
plot_it<- function(frame=dataset_name,var1){
  sum_mean <- sum_it(var1 = var1)
  it_plot <- ggplot(data=sum_mean, aes(x=Date,y=mean, colour=Trt_name, shape=Site))+
    geom_point()+
    geom_line()+ 
    geom_errorbar(aes(ymin=mean-se,ymax=mean+se))+
    facet_grid(~Site)
  
  it_plot
}


```
look at some data
```{r}
Psum <- plot_it(var1="stemGAI")

#plot_it(var1="GrainWT")


Psum
```

```{r}
 #save consist data for report and analysis
 
# # gather all variable in one column and values..
dataset_name <- "Pea_Biomass_N_LAI" # needed to name the outputfiles consistently (labels, consistent and apsim .txt)
# # # 
  SourceRootDir<- "C:\\GithubRepos\\PeaModelling\\DataConnection\\"
  DestRootDir<- "C:\\GithubRepos\\PeaModelling\\DataConnection\\"
# # # 
  cd_Path <- paste0(DestRootDir, "ObservedData_",dataset_name,".txt")
# # # 
  write.table(df_CombinedData,cd_Path , row.names = F, quote = F, sep = '\t')
# # #print(cd_Path)

```




