---
title: "Transforming Pea data into observed data for sims discovery science"
author: "R Zyskowski , Adrain Hunt"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
  github_document: default
---

## Step-2 data cleaning: Transforming  *Technically correct* (pre-processed) data to *Consistent* data

Key processes:

- Reads  *Technically correct* data into `data.frame`

- Remove missing values, correct units and add new variables.
  Change units to match APSIM-X units of each variable
  
- Data visualisation.

- Create output files:

  1. For report and analysis - i.e. file with all variables listed in a "Variables" column
  
  2. For APSIM-X input - i.e. file with each variable is a column
  
  3. Labels file for fodder beet biomass 
  


#### Data management

```{r, results='hide', echo=FALSE, include=FALSE}

rm(list=setdiff(ls(), "source_rmd")) #remove all objects but "source_rmd" from the environment before assigning the new objects .. this is especially included to use this script as a child script in the MainScript.Rmd file 

#rm(list = ls(all = TRUE))

```

Load the required libraries.


```{r, warning=FALSE}
# load the required libraries
library(lubridate)
library(plyr);library(dplyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr) #required to use the pipe (%>%) operator
library(readxl)
library(tidyverse)

```


** Set the directories**
```{r}
dataset_name <- "Pea_Biomass_N_LAI" # needed to name the outputfiles consistently (labels, consistent and apsim .txt)

SourceRootDir<- "C:\\GithubRepos\\PeaModelling\\DataConnection\\"
DestRootDir<- "C:\\GithubRepos\\PeaModelling\\DataConnection\\"

SourceData <- "18_19_SAE_pea_protein_managment.xlsx"

```





### Reads *RAW* (pre-processed) data into a `data.frame`

```{r}

library(readxl)
library(tidyverse)

scrape_xl <- function(url = NULL, sheet = NULL, skip = NULL) {
  
  # Ensure the input url is a character vector.
  stopifnot(is.character(url))
  
  # Check that the input url has the correct form.
  if (!grepl("layout", url) && !grepl(".xl", url)) {
    stop("Url is not of the correct form")
  }
  
  # Extract the base of the url.
  base_url <- url %>%
    stringr::str_split("_layouts") %>%
    lapply(`[[`, 1) %>%
    unlist()
  
  # Extract the extension of the url and replace spaces with encoded format.
  extension <- url %>%
    stringr::str_split("=/") %>%
    lapply(`[[`, 2) %>%
    unlist() %>%
    stringr::str_split(".xlsx") %>%
    lapply(`[[`, 1) %>%
    unlist() %>%
    stringr::str_replace_all(" ", "%20")
  
  # Define the correct file format to be added to the url.
  file_format <- "_layouts/download.aspx?SourceUrl=/"
  
  # Paste the base, format and extension together.
  url_fmt <- paste0(paste(base_url, extension, sep = file_format), ".xlsx")
  
  # Check that the formatted url exists and get the user credentials.
  if (httr::http_error(httr::GET(url_fmt)) == 404L) {
    stop("Url does not exist")
  }
  username <- Sys.getenv("USER")
  if (Sys.getenv("PASSWORD") == "") {
    Sys.setenv("PASSWORD" = getPass::getPass(paste0(username,
                                                    ", enter your password")))
  }
  password <- Sys.getenv("PASSWORD")
  
  # Check that the reponse had no errors with the user credentials.
  if (httr::http_error(httr::GET(url_fmt,
                                 httr::authenticate(username,
                                                    password,
                                                    type = "ntlm")))) {
    stop("The request failed, check username and password",
         httr::http_status(res))
  }
  
  # Get the response to the Excel spreadsheet and write the data to a
  # temporary file.
  httr::GET(url_fmt,
            httr::authenticate(username, password, type = "ntlm"),
            httr::write_disk(temp_file <- tempfile(fileext = ".xlsx")))
  
  # Read the Excel data in from the temp file to a dataframe.
  df <- readxl::read_excel(temp_file, sheet = sheet, skip = skip)
  
  # Return the Excel spreadsheet data from iPlant as a dataframe.
  return(df)
}

url <- "https://iplant.plantandfood.co.nz/project/P442060-13/_layouts/15/WopiFrame.aspx?sourcedoc=/project/P442060-13/Research/18_19_SAE_pea_protein_managment.xlsx&action=default"
df_RAW_HB<- scrape_xl(url, sheet =  "RAW_HB", skip = 2)

#df_RAW_HB <- read.xlsx(PreprocessedFile, sheetName = "RAW_HB", col_names = TRUE, startRow = 3, endRow=136, na = "0")

df_RAW_HB$Index  <- NULL
```


#### Inspection of loaded data set

```{r}
#Retrieve the classes of all columns in a data.frame 
sapply(df_RAW_HB, mode)
sapply(df_RAW_HB, class)
```



```{r}
str(df_RAW_HB)
```



```{r}
summary(df_RAW_HB)
```





```{r}
head(df_RAW_HB)
```


### Removing rows with NAs (missing values) in `data.frame`

```{r}
# Remove rows with NAs in data.frame
#df_HBData <- df_RAW_HB[!complete.cases(df_RAW_HB), ]
df_HBData <- df_RAW_HB
na.omit(df_HBData)

#head(df_HBData)

```



### Correcting units
Correct Biomass units from g/area to g/m2 and N conc units from % to 0-1

```{r}

#set factors as Char

df_HBData$Plot<-as.character(df_HBData$Plot)
df_HBData$Block<-as.character(df_HBData$Block)
df_HBData$Trt_num<-as.character(df_HBData$Trt_num)

 
df_HBData$partFW <- as.numeric(as.character(df_HBData$partFW)) 
df_HBData$greenleafDW <- as.numeric(as.character(df_HBData$greenleafDW)) 
df_HBData$greenleafDW[is.na(df_HBData$greenleafDW)] <- 0 

df_HBData$greenstemDW <- as.numeric(as.character(df_HBData$greenstemDW)) 
df_HBData$greenleafDW[is.na(df_HBData$greenleafDW)] <- 0 
df_HBData$deadDW <- as.numeric(as.character(df_HBData$deadDW)) 
df_HBData$deadDW[is.na(df_HBData$deadDW)] <- 0 
df_HBData$greenpodDW <- as.numeric(as.character(df_HBData$greenpodDW)) 
df_HBData$greenpodDW[is.na(df_HBData$greenpodDW)] <- 0 
df_HBData$maturepodDW <- as.numeric(as.character(df_HBData$maturepodDW)) 
df_HBData$maturepodDW[is.na(df_HBData$maturepodDW)] <- 0 
df_HBData$grainDW <- as.numeric(as.character(df_HBData$grainDW)) 
df_HBData$grainDW[is.na(df_HBData$grainDW)] <- 0 
df_HBData$maturegrainDW <- as.numeric(as.character(df_HBData$maturegrainDW)) 
df_HBData$maturegrainDW[is.na(df_HBData$maturegrainDW)] <- 0 

df_HBData$N_Content_Green_Leaf[df_HBData$N_Content_Green_Leaf == "-"] <- NA 

df_HBData$N_Content_Green_Leaf <- as.numeric(as.character(df_HBData$N_Content_Green_Leaf)) 

df_HBData$N_Content_Green_Stem[df_HBData$N_Content_Green_Stem == "-"] <- NA 

df_HBData$N_Content_Green_Stem <- as.numeric(as.character(df_HBData$N_Content_Green_Stem)) 

df_HBData$N_Content_Green_Grain[df_HBData$N_Content_Green_Grain == "-"] <- NA 
df_HBData$N_Content_Green_Grain <- as.numeric(as.character(df_HBData$N_Content_Green_Grain)) 
df_HBData$N_Content_Mat_Grain[df_HBData$N_Content_Mat_Grain == "-"] <- NA 
df_HBData$N_Content_Mat_Grain <- as.numeric(as.character(df_HBData$N_Content_Mat_Grain)) 


for (k in 1:length(df_HBData$TFW2) )
 {
  if (is.na(df_HBData$TFW2[k]))
      {
      df_HBData$TFW2[k] = df_HBData$TFW[k] 
      }
  if (isTRUE( df_HBData$Final_residueFW[k] > 0) )       
   {
    df_HBData$partFW[k] = ((df_HBData$Final_residueFW[k] + df_HBData$Final_podFW[k] +df_HBData$Final_grainFW[k]))
   }
 }

#Biomass
df_HBDataMod <-  df_HBData %>%
   mutate(perM = (TFW2/partFW/HA)) %>%
   mutate(partDW = (greenleafDW + greenstemDW + deadDW  + greenpodDW + maturepodDW + grainDW + maturegrainDW)) %>%
   mutate(FieldPea.AboveGround.Wt = (perM*partDW) )%>%
  mutate(FieldPea.leaf.Live.Wt = perM*(greenleafDW)) %>%
   mutate(FieldPea.Stem.Live.Wt = perM*(greenstemDW)) %>%
  mutate(FieldPea.Dead.Wt = perM*(deadDW)) %>%
   mutate(FieldPea.Pod.Live.Wt = perM*(greenpodDW)) %>%
   mutate(FieldPea.Grain.Mature.Wt = perM*(maturegrainDW)) %>%
 
  mutate(FieldPea.Grain.Live.Wt = perM*(grainDW)) %>%
   mutate(FieldPea.leaf.LeafArea = perM*(Leaf_area)) %>%
  mutate(FieldPea.leaf.LAI = Leaf_area/FieldPea.leaf.Live.Wt)

df_HBDataMod <-  df_HBDataMod %>%
  mutate(FGW = Final_100grainDW*Final_grainFW/Final_100grainFW/HA)

df_HBDataMod$FGW <- as.numeric(as.character(df_HBDataMod$FGW)) 
df_HBDataMod$FGW[is.na(df_HBDataMod$FGW)] <- 0 


df_HBDataMod <-  df_HBDataMod %>%
  mutate(GrainWT =  FieldPea.Grain.Live.Wt+FieldPea.Grain.Mature.Wt+ FGW)

#for (k in 1:length(df_HBDataMod$FGW) )
# {
#  if (is.numeric(isTRUE(df_HBDataMod$FGW) == TRUE))
#       df_HBDataMod$FieldPea.Grain.Mature.Wt[k] = df_HBData$FieldPea.Grain.Mature.Wt[k] + df_HBDataMod$FGW[k]
#}

#N content  
  
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.leaf.NConc = N_Content_Green_Leaf/100.0)
 
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.leaf.N = FieldPea.leaf.NConc * FieldPea.leaf.Live.Wt )
   
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Stem.NConc = N_Content_Green_Stem/100.0)
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Stem.N = FieldPea.Stem.NConc * FieldPea.Stem.Live.Wt )

 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.NConc = N_Content_Green_Grain/100.0)
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.Live.N = FieldPea.Grain.NConc * FieldPea.Grain.Live.Wt )
  df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.Mature.NConc = N_Content_Mat_Grain/100.0)
 df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.Mature.N = FieldPea.Grain.Mature.NConc * FieldPea.Grain.Mature.Wt )

 
#protein 
df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.Mature.Protein = (FieldPea.Grain.Mature.NConc *GrainWT) *6.25 )

df_HBDataMod <-  df_HBDataMod %>%
    mutate(FieldPea.Grain.Live.Protein = (FieldPea.Grain.NConc *GrainWT) *6.25 )

df_HBDataMod$FieldPea.Grain.Protein = df_HBDataMod$FieldPea.Grain.Mature.Protein


for (k in 1:length(df_HBDataMod$FieldPea.Grain.Protein) )
 {
  if (is.na(df_HBDataMod$FieldPea.Grain.Protein[k]))
  {
    df_HBDataMod$FieldPea.Grain.Protein[k] = df_HBDataMod$FieldPea.Grain.Live.Protein[k] 
  }
}
 


head(df_HBDataMod)
summary(df_HBDataMod)

```

### Create a summary file

```{r}

df_HBDataSum<- df_HBDataMod %>% 
  group_by(Date,Trt_name) %>%  

  summarise_if(is.numeric,funs(mean,se=sd(.)/sqrt(n())))
  
   
summary(df_HBDataSum)


```


### Convert date format and sort out factors

```{r}

df_HBDataSum <- df_HBDataSum %>%
  # Convert date format
  mutate(Clock.Today = ymd(Date))

# Sort out factors

```


### Inspect the latest `data.frame` of ConsistData

```{r}
str(df_HBDataSum)
```


```{r}
head(df_HBDataSum)
```


```{r}
summary(df_HBDataSum)
```

### Data visualisation - exploratory graphs

```{r, fig.width = 12}
df_HBDataSum %>%
 ggplot(aes(x=Clock.Today,y=(FieldPea.leaf.Live.Wt_mean),colour=Trt_name, linetype=Trt_name,shape=Trt_name)) +
  geom_point(size=2,alpha=0.5) +
  geom_line() +
  ylab("g/m2")+
  geom_errorbar(aes(ymin=FieldPea.leaf.Live.Wt_mean-FieldPea.leaf.Live.Wt_se, ymax=FieldPea.leaf.Live.Wt_mean + FieldPea.leaf.Live.Wt_se))
 
```


```{r}
df_HBDataSum %>%
  mutate(Trt_num =factor(Trt_num, levels=c(1:6))) %>%
  ggplot(aes(x=Clock.Today,y=(FieldPea.Stem.Live.Wt),colour=Block, linetype=Trt_num,shape=Trt_num)) +
  geom_point(size=2,alpha=0.5) +
  geom_line() +
  ylab("g/m2") 

```

#### Compare N% and biomass in a Grain
```{r}
df_HBDataSum %>%
  mutate(Trt_num =factor(Trt_num, levels=c(1:6))) %>%
  ggplot(aes(x=Clock.Today,y=(FieldPea.Grain.Protein),colour=Block, linetype=Trt_num,shape=Trt_num)) +
  geom_point(size=2,alpha=0.5) +
  geom_line() +
  ylab("g/m2") 

```
```{r}
df_HBDataSum %>%
  mutate(Trt_num =factor(Trt_num, levels=c(1:6))) %>%
  ggplot(aes(x=Clock.Today,y=(FieldPea.Grain.Mature.NConc),colour=Block, linetype=Trt_num,shape=Trt_num)) +
  geom_point(size=2,alpha=0.5) +
  geom_line() +
  ylab("g/m2") 
```

### Save Consistent Data

** 1. Save *Consistent* data for report and analysis ** 
```{r}
#save consist data for report and analysis

# gather all variable in one column and values..

cd_Path <- paste0(DestRootDir, "ObservedData_",dataset_name,".txt")

write.table(df_HBDataSum,cd_Path , row.names = F, quote = F, sep = '\t')
print(cd_Path)

```


** 2. Save *Consistent* data for APSIM-X **
```{r}
#drop units columns that will be added later....
#df_forAPSIM <- df_ConsistData_latest %>%
 # mutate(Irr=factor(Irr),Nit=factor(Nit)) %>%
 # mutate(Clock.Today=as.Date(ymd(Clock.Today))) %>%
 # mutate(Clock.Today=as.character(as.Date(Clock.Today, "%Y-%m-%d"))) %>%
#  dplyr::select(-Plot,-Block,-Nit,-Irr,-Code) %>%
#  group_by(Clock.Today,SimulationName) %>%
#  summarise_all(funs(mean)) %>%
#  mutate(SimulationName = factor(SimulationName))%>%
 # ungroup()%>%
 # as.data.frame()

#summary(df_forAPSIM)

```

Save *Consistent* data for APSIM-X
```{r}
#save consist data for APSIM-X
#apx_Path <- paste0(FileSaveDir_APSIM, "/OBS_",dataset_name,".txt")
#write.table(df_forAPSIM, apx_Path, row.names = F, quote = F, sep = '\t')
```


## Get and view units for both Field and APSIM

```{r}
#dfTemp1_lbs <- read.xlsx(PreprocessedFile, sheetName = "lookupVariables") # no need to inlcude `col_names = TRUE` - Mei 22/5/2018

# remove NA rows 

#dfTemp1_lbs <- dfTemp1_lbs[complete.cases(dfTemp1_lbs), ]

#look at df
#dfTemp1_lbs

# for all cols to factors - this step not needed, Mei 22/5/2018
#cols <- colnames(dfTemp1_lbs)
#dfTemp1_lbs[cols] <- lapply(dfTemp1_lbs[cols], factor)


# remove unnecessary fields i.e. Drop data frame columns by name
#drops <- c("Name_Field", "Units_Field") # "col_names" has been excluded now, so no need to inlcude in drops - mei
#dfTemp1_lbs <- dfTemp1_lbs[ , !names(dfTemp1_lbs) %in% drops]


#head(dfTemp1_lbs, nrow(dfTemp1_lbs)) #FIXME: need to remove unwanted col 'col_names' which was added during factor conversion! (done? - eit); Done, see above codes - Mei 22/05/2018

```


## Incoporate missing labels

```{r}
#get variables from df_forAPSIM to list as labels names under colname of `Name_APSIM` in data frame dfTemp2_lbs
#dfTemp2_lbs <- data.frame(Name_APSIM = colnames(df_forAPSIM))

#get rows those are NOT found in dfTemp1_lbs  col `Name_APSIM` thus avoiding duplicates
#dfTemp2_lbs <- anti_join(dfTemp2_lbs, dfTemp1_lbs, by = "Name_APSIM")


#dfTemp2_lbs  #look at df to see any unwanted rows to drop
# drop unwanted rows

#dropRows <- c("SimulationName")

#dfTemp2_lbs <- dfTemp2_lbs %>%
#  filter(!Name_APSIM %in% dropRows)

#add Units_APSIM and VarClass
#dfTemp2_lbs <- dfTemp2_lbs %>% 
#   mutate(Units_APSIM = ifelse(grepl('.Wt', Name_APSIM), yes = "g/m2", no = "fractional")) %>%  
 #  mutate(VarClass = ifelse(grepl('.Wt', Name_APSIM), yes = "Biomass", no = "PlantN")) 
   
#To keep all rows from both data frames in a final df for labels
#labelsFinal <- merge(dfTemp1_lbs, dfTemp2_lbs, all = TRUE) 

#print(labelsFinal)
```


### save labels

```{r}
#save labels in txt file
#txtFilePath <- paste0("K:/Rainshelter/MultiCropRotation_APSIM_X/Labels/LBS_",dataset_name,".txt") 

# save to unit labels
#write.table(labelsFinal,
#            txtFilePath, 
#            row.names = F, quote = F, sep = '\t')
```

